Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-03 paper/paper.tex
pass on sections III, IV.B, and first par. section V

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

Figure~\ref{fig:workflow} illustrates the infrastructure we used for
differential testing, which is related to part of the study discussed
in this paper.  The bug-finding process takes on input JS files from
regression test suites of various JS engines and generates warnings on
output. Boxes in the figure denote encapsulation; arrowed lines
indicate data flow. The cycle icons denote repetition--the leftmost
icon indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.

New inputs are obtained for a given test input using some
off-the-shelf input fuzzer~\cite{fuzz-testing-history}.\Comment{
  Several fuzzing methods have been proposed in the past, varying with
  respect to how new inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Note that a number of reasons exist, other than a bug, to
explain discrepancy (see Table~\ref{tab:false-positives}). We used the
open-source eshost-cli project~\cite{eshost-cli} for checking output
discrepancy. Microsoft uses that tool in the Chakra JS engine.

@@

Recall that a warning can be results of various causes other than a
bug (see Table~\ref{tab:false-positives}). To facilitate inspection,
the infrastructure groups and prioritize these warnings. Considering
prioritization, we classified warnings in two kinds, reflecting their
likelihood to manifest a real bug. Warnings of the kind ``\hi{}'' are
associated with the cases where the anomaly has been detected in the
execution of the test code or its harness. The rationale is that the
test in this group executed without violating any internal checks of
the API. In constrast, warnings in the ``\lo{}'' group reflect the
cases where the anomaly was observed during the execution of functions
not related to the test itself. We found that different engines often
check pre-conditions of those functions differently. It can happen,
for example, that one engine enforces a weaker pre-condition compared
to another and that is acceptable.\Mar{example!} In those cases, our
infrastructure would observe a discrepancy that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
a bug in the test not the code. Although we did find real bugs from
``\lo{}'' warnings, the proportion was much lower compared to
``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
found originated from ``\lo{}'' warnings.

@@

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the offical
TC-39~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. We did not consider tests from the \chakra{}
repository because of their intensive use of Chakra-specific
objects. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Overall, we found a total of \totfiles{} JS files.

It is also worth mentioning that some engines use custom shell,
including a harness with custom assertions, to run tests.  For these,
we needed to make small changes in the testing infrastructure to be
able to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable harness functions, which are only
available to certain engines.

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strenght of the approach is
limited by the supported mutation operators, which are typically
simple, and the quality of the test suite. We chose \radamsa\ and
\quickfuzz\ \Fix{...elaborate...}

@@

Recall that the goal of our study is to assess reliability of
\js\ engines by leveraging implementation diversity, which is
specially rich in this domain. We report results in three
parts. First, we report on the stability of the engines we analyzed
using the Test262 standard conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}. The intuition is that the
bugs we discover throughout this study would have low relevance if the
engines are too fragile. Second, we report results obtained with test
transplantation. The hypothesis is that test cases written for one
engine may reveal bugs in different engines. The rationale is that the
domain of possible inputs is too large; consequently, we expect that
test suites of a given engine cover scenarios and corner cases
uncovered by another engine. Third, we analyzed the impact of using
cross-engine differential testing to find bugs. The hypothesis is that
even black-box fuzzers can expose important bugs.

@@

\subsection{Cross-Engine Differential Testing}

>>>>

Figure~\ref{fig:workflow} illustrates the infrastructure we used for
differential testing, use in part of our study. The bug-finding
process takes on input JS files from regression test suites of various
JS engines and generates warnings on output. Boxes in the figure
denote encapsulation; arrowed lines indicate data flow. The cycle
icons denote repetition--the leftmost icon indicates that each file in
the input list will be analyzed in separate whereas the rightmost icon
shows that a single file will be fuzzed multiple times.

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[h]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Note that a number of reasons exist, other than a bug, to
explain discrepancy (see Table~\ref{tab:false-positives}). We used the
open-source eshost-cli project~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distiguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups. Considering prioritization, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is valid--considering the checks declared
in the API functions--but, still, it manifests discrepancy through
violation of an assertion declared in the test.\Mar{example!} In constrast, warnings
in the ``\lo{}'' group reflect the cases where the anomaly was
observed during the execution of functions not related to the test
itself. We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition on a function input compared to
another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
observe a discrepancy that is more likely to be associated with an
invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
in the test code not the engine (library or runtime) code. Although we
did find real bugs from ``\lo{}'' warnings, the proportion was much
lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
reals bugs we found originated from ``\lo{}'' warnings.

@@

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the offical
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. We did not consider tests from the \chakra{} repository because
they depend on non-portable objects. Notice that the number of tests
in \veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The \veight{} test
suite contains other tests, but, as in \chakra{}, these tests use
non-portable testing objects that we still did not mock.

It is also worth mentioning that some engines use a custom shell to
run tests, including a harness with specific assertions.  For these,
we needed to make small changes in the testing infrastructure to be
able to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable harness functions, which are only
available to certain engines.

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strenght of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose \radamsa\ and
\quickfuzz\ \Fix{...elaborate...} \Mar{I mention below that these
  fuzzers ``only make valid changes in literals of the
  language''. Please confirm and explain that still this is
  interesting!}

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity, which is specially rich in this
domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the Test262 standard
conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we hope that that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms such as those that
could emerge from implementation-dependent behavior. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typicaly make valid
changes only in literals of the language could expose important
bugs. All in all, we want to assess the impact of simple approaches
that leverage on diversity to find bugs in \js\ engines with the goal
of assessing their reliability.

@@

\subsection{Cross-Engine Differential Testing}
\label{sec:cross-engine-diff-testing-results}
